---
title: "Title of the report"
author: "Course Quality Advisory Board"
date: "September 2, 2015"
output: html_document
---

```{r, echo = FALSE}
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(likert)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
suppressWarnings(suppressPackageStartupMessages(library(scales)))
suppressWarnings(suppressPackageStartupMessages(library(psych)))
suppressWarnings(suppressPackageStartupMessages(library(grid)))
suppressWarnings(suppressPackageStartupMessages(library(RColorBrewer)))
suppressWarnings(suppressPackageStartupMessages(library(xtable)))
suppressWarnings(suppressPackageStartupMessages(library(tidyr)))

library(knitr)
library(markdown)
library(rmarkdown)
library(dplyr)
library(likert)
library(scales)
library(psych)
library(reshape)
library(grid)
library(RColorBrewer)
library(xtable)
library(tidyr)
options(xtable.comment = FALSE)
```

#Introduction
##Course Quality Advisory Board
C-QAB is a voluntary student organization comprised of current and past Erasmus Mundus students. The focus of C-QAB is to facilitate communication between the Association and the Erasmus Mundus programmes. C-QAB accomplishes this by coordinating the EMA Programme Representatives, conducting an annual student services satisfaction survey and responding to student concerns through its email account. 

If you have any concerns or would like to request some additional information, feel free to contact us through e-mail: em.feedback@em-a.eu.

##Some stuff about the survey
Number of respondents, number of courses with 10+ respondents, tables with coverage and response rates.

##Structure of the document

This report is structured similar to a survey itself. There are four sections each represented by multiple questions. Each individual question is explained through a graph and a table. 

Graph plots the responses from students, while table provides information about how other courses did on that question. Example of a table below:

```{r, warning=FALSE, echo=FALSE, results='asis'}
df <- comparative_df(questions[1], course_dataset)
z <- xtable(df, caption = sprintf("Summary statistics for %s question", questions[1]), digits = c(0,0,2,2,2,2,2,2,2), type = "html")
align(z) <- "|p{5.5cm}|cc|c|lllll|"
print(z, table.placement="h", floating = FALSE)
```

Each row represents a dimension of the question. It contains information about the mean that question received from students of your program. Following that is the mean for all respondents of the survey. Finally, table provides information about distribution of means in all other courses. Distribution is represented by quantiles. This means that 25% of courses will lie between two adjacent columns (e.g., 0%-25%). This enables easy comparison of any given program with its peers.

Important note: Throughout this report only dimensions with at least 10 respondents will be used. That means that for some dimensions, instead of a mean, there will be a special value NA (not available). We still keep the comparative information for that dimension for reference.

## Executive summary (?)

#Supporting services

```{r, echo = FALSE, warning=FALSE, fig.height=4, results = "asis"}
report_question("B.1.1", course_dataset)
```

```{r, echo = FALSE, warning=FALSE, fig.height=4, results = "asis"}
report_question("B.1.3", course_dataset)
```

```{r, echo = FALSE, warning=FALSE, fig.height=4, results = "asis"}
report_question("B.2.1", course_dataset)
```

```{r, echo = FALSE, warning=FALSE, fig.height=4, results = "asis"}
report_question("B.2.2", course_dataset)
```

#Assessment and feedback
Some introductory text about the section

```{r, echo = FALSE, warning=FALSE, fig.height=4, results = "asis"}
report_question("C.1", course_dataset)
```


#Thesis supervision and personal development
Some introductory text about the section

#Internship/field experience
Some introductory text about the section

#Information about specific universities
Some introductory text about the section

##First university
Table with universities that were "first"

##Second university
Table with universities that were "second"

##Third university
Table with universities that were "third"

##Fourth university
Table with universities that were "fourth"

#Concluding remarks
Some concluding remarks