---
title: "CQSS 2015"
author: "Mikhail Balyasin"
date: "May 20, 2016"
output: 
  html_document:
    toc: true
---

```{r echo = FALSE}
library(googleVis)
library(DT)
library(plotly)
library(reshape2)
op <- options(gvis.plot.tag='chart')
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, results = 'asis', fig.width = 10)
```

##Introduction

##Forward

##Course Quality Advisory Board

##Overview of Survey and Report

##Overview of EMJMD Programs
- Brief statement of what EMJD programs are and which ones were analyzed in the survey (list them and/or map them?)

- Which universities were involved and geographical location (perhaps add a map localizing all the universities?)

###Nationalities
```{r nationalities, results='asis', tidy=FALSE, echo = FALSE}
overalldf <- overall %>%
  select(A.7.What.is.nationality.please.choose.one.only._Response) %>%
  group_by(A.7.What.is.nationality.please.choose.one.only._Response) %>%
  summarise(respondents = n())
names(overalldf) <- c("Country", "respondents")
overalldf <- overalldf[complete.cases(overalldf$Country),]

Geo <- gvisGeoChart(overalldf, colorvar = "respondents", locationvar = "Country")
plot(Geo)
```

###Gender
```{r gender, results = "asis", tidy=FALSE, echo = FALSE, warning=FALSE}
gender <- as.data.frame(summary(overall$A.9.Gender._Response))
names(gender) <- c("Number")
DT::datatable(gender,options = list(dom = 't', searching = FALSE,
                                                    columnDefs = list(list(width = "190px", targets = "_all")),
                                                    align = "center"
                                                    ))

```

###Age
```{r age, echo = FALSE}
ggplotly(qplot(overall$A.8.Age._Response))

```

###Disability
```{r disability, results = "asis", echo = FALSE}
disability <- as.data.frame(summary(overall$A.12.Do.you.have.any.diagnosed.disability._Response))
names(disability) <- c("Number")
DT::datatable(disability,options = list(dom = 't', searching = FALSE,
                                                    columnDefs = list(list(width = "190px", targets = "_all")),
                                                    align = "center"
                                                    ))

```

###Start year of studies
```{r year, results = "asis", echo = FALSE}
year <- as.data.frame(summary(as.factor(overall$A.5.When.did.you.start.EM.Course._Response)))
names(year) <- c("Number")
DT::datatable(year,options = list(searching = FALSE,
                                                    columnDefs = list(list(width = "190px", targets = "_all")),
                                                    align = "center"
                                                    ))

```

###Programs with 10 or more respondents
```{r programs, results = "asis", echo = FALSE}
DT::datatable(tenormore,options = list(searching = FALSE,
                                                    columnDefs = list(list(width = "190px", targets = "_all")),
                                                    align = "center"
                                                    ), rownames = FALSE)

```

###Scholarship
```{r scholarship, results = "asis", echo = FALSE}
scholarship <- as.data.frame(summary(as.factor(overall$A.10.Have.you.been.awarded.an.Erasmus.Mundus.scholarship.for.master.studies._Response)))
names(scholarship) <- c("Number")
DT::datatable(scholarship, options = list(dom = 't', searching = FALSE,
                                                    columnDefs = list(list(width = "190px", targets = "_all")),
                                                    align = "center"
                                                    ))

```



##Supporting services

###Support received before the start of the programs
```{r supp_before}
z <- gsub("2004|2005|2006|2007|2008|2009|2010|2011", "Alumni", overall$A.5.When.did.you.start.EM.Course._Response)
levels <-c("Alumni", "2012", "2013", "2014") 
z <- factor(z, levels = levels)
ggplotly(means_printing("B.1.1"))
```
```{r supp_before_group, fig.height=8}
questionprint_grouping("B.1.1", overall, grouping = z, grouping_levels = levels)

```


###Support received during orientation program
```{r orientation}
ggplotly(means_printing("B.1.3"))
```

```{r orientation_group, fig.height=10}
questionprint_grouping("B.1.3", overall, grouping = z, grouping_levels = levels)

```


###Helpfulness of units and people
```{r helpfulness}
ggplotly(means_printing("B.2.1"))

```
```{r helpfulness_group, fig.height=10}
questionprint_grouping("B.2.1", overall, grouping = z, grouping_levels = levels)

```


###Support received on various issues
```{r support_on}
ggplotly(means_printing("B.2.2"))
questionprint_grouping("B.2.2", overall, grouping = z, grouping_levels = levels)

```

##Assessment and Feedback

###Module assessment
```{r module_asses}
ggplotly(means_printing("C.1"))

```
```{r module_asses_group, fig.height=12}
questionprint_grouping("C.1", overall, grouping = z, grouping_levels = levels)

```

##Teaching/Learning and Supervision

###Teaching/Learning across different universities

###First supervisor
```{r first_sup, fig.height=4}
ggplotly(means_printing("L.4"))
questionprint_grouping("L.4", overall, grouping = z, grouping_levels = levels)
```


###Second supervisor
```{r second_sup, fig.height=4}
ggplotly(means_printing("L.5"))
questionprint_grouping("L.5", overall, grouping = z, grouping_levels = levels)

```


##Internship/Field Experience and Personal Development

###Personal development
```{r development}
ggplotly(means_printing("L.6"))
```
```{r development_group, fig.height=10}
questionprint_grouping("L.6", overall, grouping = z, grouping_levels = levels)

```

###Field experience
```{r field}
ggplotly(means_printing("L.3.a"))
```
```{r field_group, fig.height=10}
questionprint_grouping("L.3.a", overall, grouping = z, grouping_levels = levels)

```

###Internship experience
```{r internship}
ggplotly(means_printing("L.2.a"))
```
```{r internship_group, fig.height=10}
questionprint_grouping("L.2.a", overall, grouping = z, grouping_levels = levels)

```

##Additional Remarks

##Conclusion/Discussion