---
title: "`r as.character(tenormore$Course[i])`"
date: "Report was generated on `r today_date`"
output: 
  pdf_document:
    includes:
      before_body: header.tex
toc: yes
numbersections: yes
fig_caption: true
header-includes:
    - \usepackage{colortbl, xcolor, titling, fancyhdr}
    - \setlength{\tabcolsep}{3pt}
    - \definecolor{table-hl}{RGB}{90, 180, 172}
    - \pagestyle{fancy}
    - \lfoot{\includegraphics[width=0.75cm]{logo_ema.png}}
    - \cfoot{\fontsize{8}{12} \selectfont `r as.character(tenormore$Course[i])`}
    - \rfoot{\thepage}  
    - \input{header}
---

```{r, echo = FALSE}
#headers - http://tex.stackexchange.com/questions/139139/adding-headers-and-footers-using-pandoc
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(likert)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
suppressWarnings(suppressPackageStartupMessages(library(scales)))
suppressWarnings(suppressPackageStartupMessages(library(psych)))
suppressWarnings(suppressPackageStartupMessages(library(grid)))
suppressWarnings(suppressPackageStartupMessages(library(RColorBrewer)))
suppressWarnings(suppressPackageStartupMessages(library(xtable)))
suppressWarnings(suppressPackageStartupMessages(library(tidyr)))
suppressWarnings(suppressPackageStartupMessages(library(rmarkdown)))

library(knitr)
library(markdown)
library(rmarkdown)
library(dplyr)
library(likert)
library(scales)
library(psych)
library(reshape)
library(grid)
library(RColorBrewer)
library(xtable)
library(tidyr)
options(xtable.comment = FALSE)
opts_knit$set(progress = F, verbose = F)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, results = 'asis')
```

\pagebreak

\textbf{Foreword}

The present report was compiled by the Course Quality Advisory Board (CQAB) of the Erasmus Mundus Student and Alumni Association (EMA) with the main purpose of providing Erasmus Mundus Joint Master Degree (EMJMD) courses with customized student feedback that emerged from the 2015 edition of the Course Quality Student Services (CQSS) survey. This feedback can aid courses in their quest of **improving student services**, and **benchmark** against other course in the Erasmus Mundus umbrella. 

The CQSS survey reached its **second edition**. The current edition of the survey brings a number of improvements. Many of these **improvements emerged from the feedback provided by EMJMD consortia** following the release of the previous CQSS survey reports, and **Erasmus Mundus students**. At the recommendation of EMJMD consortia, the course reports now include **comparative information** about each course in relation to the other EMJMD courses that received a sufficient number of responses. At the suggestion of survey respondents, the 2015 CQSS survey edition was released at the end of the academic year, to ensure that all respondents have completed at least two EMJMD semesters before being asked to evaluate their experience. Additional changes have been made to the 2015 edition of the CQSS survey to streamline the survey experience, to facilitate the data analysis process, and to capture information about key subpopulations among EMJMD students.  For further reference, a **full description of the methodology** behind the creation of the 2015 edition of the CQSS survey and the analysis procedures behind the CQSS reports is going to be published in the first 2016 edition of the academic journal Education Studies Moscow.

Due to our responsibility towards the entire EMJMD community and the over 2000 students and alumni that fully completed our lengthy survey, **the results emerging from the 2015 edition of the CQSS survey will be made available to the broad public on an interactive online platform**. The online platform will contain the graphical information included in this report, and be made available online shortly after the distribution of course reports to EMJMD consortia. By making this information public, CQAB does not aim at classifying or creating rankings among EMJMD courses, but to add transparency to our data analysis, and offer current and prospective students the ability to better prepare for what CQAB considers to be an invaluable educational experience.

The work of CQAB would not exist and could not continue **without the support of numerous committed volunteers spread all across the world**, driven by a strong motivation to help improve the quality of EMJMD courses. During the last 18 months, over 40 volunteers were involved with different stages of the CQSS project, from analyzing feedback received following the 2013 edition of the CQSS survey, to coding qualitative data and interpreting descriptive graphical information. **CQAB is grateful, humbled and proud to have supported the CQSS project fully through volunteer work**, and thus without external interference. 

Among the CQAB volunteers, two stand out: Mikhail Balyasin and Luis Carvalho. Mikhail is responsible for the substantial improvements to the design and content of course reports, has skilfully generated the graphical information made available in this report, and created the CQSS interactive online platform. Luis coordinated the process of analyzing the vast qualitative data that emerged from the CQSS survey, rethought the architecture of the CQSS survey and helped streamline the survey experience for respondents.

CQAB is grateful for the ongoing support received from the **Erasmus Mundus Student and Alumni Association, and its leadership structures**. We are indebted to representatives of the **European Commission**, and EMJMD course coordinators whom we consider allies in a joint quest of consolidating the excellence brand of EMJMDs.

CQAB is eager to receive further feedback from each course coordinator and other stakeholders on how future CQSS reports and their contents may be improved in order to maximize their usefulness. We understand that courses themselves are best suited to address quality concerns, and we strongly suggest that the information in report, with its limitations, is triangulated with internally available data at the level of each course. 

Please address all questions and remarks about this report to Georgiana Mihut at cqab.chair@em-a.eu.

With gratitude and hope for a fruitful future collaboration, 

**Georgiana Mihut**, Chair of the Course Quality Advisory Board

#Course Quality Advisory Board
CQAB is an independent advisory body that operates on a voluntary basis as part of the Erasmus Mundus Student and Alumni Association. Its members have not and do not receive financial benefits as a result of their CQAB related activities. Membership to CQAB is assured through a competitive recruitment process among EMA members. Internally, CQAB has three main separate structures: 

   1. Management of the e-mail account \textbf{em.feedback@em-a.eu}, that assists students with pressing quality issues;
   2. **Survey Team**, tasked with conducting the CQSS survey;
   3. **Communication Team**, a newly created structure aimed at facilitating the promotion of CQAB activities.
  
CQAB was created as a result of the pressing and constant concerns of EMA members about the quality of the student experiences as part of an Erasmus Mundus course. Internally, CQAB has a variety of tools to capture student concerns and to interact with student representatives from various programmes, but the CQSS survey represents its most comprehensive and systematic initiative focused on quality assurance. The inception and design of the CQSS survey is enrooted in the complexity of the EMJMD student experience and driven by two distinct factors: the perceived systemic yet unique issues around quality across joint degree courses, and the general underrepresentation of students in the systemic evaluation of the EMJMD programme.

\pagebreak

#Introduction to the current report

This report introduces three distinct sources of information. First, it aims to bring to your attention the **`r nrow(course_dataset)` responses** received from current or past students of `r as.character(tenormore$Course[i])`. The respondents represent **`r length(unique(course_dataset$A.7.What.is.nationality.please.choose.one.only._Response))` distinct nationalities**. Collectively they have spent more than **`r as.numeric(round(sum(as.POSIXct(course_dataset$EndDate_) - as.POSIXct(course_dataset$StartDate_))/60))` hours** answerring and thinking about the survey questions. The responses are introduced in graphical form for each indicator and dimension captured in the CQSS survey that received 10 or more responses. The graphical information follows the structure illustrated in Figure 1, where the name of the dimension (and often the name of the survey question) appears as a figure header (in this case **Overall satisfaction**), and each indicator is displayed on a separate row. The figure illustrates the proportion of respondents that selected each of the four Likert scale options available. Figure 1 illustrates the actual overall satisfaction of respondents with the course.

```{r}
z <- c("C.3.Please.rate.academic.satisfaction.with.EM.course._", 
       "C.4.Please.rate.overall.satisfaction.with.EM.course._")
question <- course_dataset[, z]
names(question) <- c("Overall academic satisfaction", 
                     "Overall satisfaction")

individual_universities <- prepare_university("N.5.1", course_dataset)

for(i in seq_along(as.character(unique(individual_universities$University.1)))) {
  temp <- individual_universities[individual_universities$University.1 == as.character(unique(individual_universities$University.1))[i],]
  names(temp)<- c("University.1", as.character(unique(individual_universities$University.1))[i])
  temp$University.1 <- NULL
  question <- as.data.frame(cbind.fill(question, temp))
}
for(i in seq_along(question)) {
  ### this step will also reduce all other answers to NA's
  question[,i] <- factor(question[,i], levels = likert_levels)
}
question <- question[, colSums(!is.na(question)) >= 10]
```
```{r, fig.height = 1 + 0.4*ncol(question)}
p <- plot_question(question, "Overall satisfaction")
plot(p)
```

\begin{center}
Figure 1: Example of graphical distribution of survey responses
\end{center}

Second, for each indicator evaluated through the CQSS survey, comparative data on the aggregated performance among all EMJMD courses with 10 or more responses is introduced (see Table below). 

```{r}
df <- comparative_df(questions[1], course_dataset)
df <- df[1:3,]
z <- xtable(df, digits = c(0,0,2,2,2,2,2,2), type = "html")
align(z) <- "|p{5cm}|cc|c|cccc|"
print(z, table.placement="h", floating = TRUE, NA.string = "NA", sanitize.text.function = function(x) x)
```

Each row in Table above represents a distinct indicator evaluated as part of the CQSS survey. Each table includes all indicators which received 10 or more responses and compose a dimension. Tables include 

  a. The number of responses received for each indicator (n); 
  b. The mean for each indicator corresponding to focus course of the report (Mean);
  c. The aggregated mean for the respective indicator across all EMJMD courses (EM mean). 

Additionally, the table provides information about the distribution of means across all EMJMD courses with 10 or more responses. The distribution of means is displayed as ranges of means in quartile increments. As such, 25% of all EMJMD courses with 10 or more responses will be found in each of the four columns. The quartile corresponding to the course profiled in each report is highlighted. This display facilitates an easy comparison between a given programme and its peers. The means displayed in the comparison tables are obtained by converting Likert-scale survey responses to numeric values. CQSS respondents were asked to evaluate each indicator on a four point Likert-scale, from "Very unsatisfied" or "Disagree" to "Very satisfied" or "Agree". For the purpose of the means utilized in this report, each Likert-scale option corresponds to the following numeric values: 

  a. "Very unsatisfied" or "Disagree" = 1;
  b. "Unsatisfied" or "Somewhat disagree" = 2;
  c. "Satisfied" or "Somewhat agree" = 3;
  d. "Very satisfied" or "Agree" = 4.

Therefore, the average score for any given indicator in a table ranges from a minimum of 1 to a maximum of 4, where 4 represents a perfect score for an indicator.

Third, few of the sections of the report introduce an overall description of the qualitative analysis of relevant open ended questions the CQSS survey asked. These selected sections do not pertain solely to the qualitative answers received for `r as.character(tenormore$Course[i])`, but instead offer the range of positions and issues discussed freely be respondents across all EMJMD courses. These sections aim to serve as a source of reference and narratives to better understand the statistical data presented. 

The information in this report is introduced following the structure employed by the CQSS survey. Through its design, the CQSS survey aims at capturing both the **overall experience** of students within an EMJMD, and the experience students had independently at **each institution attended**. To reflect this dichotomy, each section of the report will introduce both the **overall evaluation of an indicator**, as reflected by respondents, and **the evaluation of the same or comparable indicator in the context of different universities attended**. The most extensive section of the report focuses on providing information about the **supporting services available to students**. The evaluation of the quality of supporting services available to students is broken down between the evaluation of:

  1. Support structures received before the start of the EMJMD programme;
  2. Support structures received during the orientation programme;
  3. The general helpfulness of various units and individuals;
  4. Support received on various specific student issues. 

The following section of the report introduces the indicators used to capture the quality of the assessment and feedback processes. Next, the responses of students to questions pertaining to the quality of teaching, learning and supervision are presented. Lastly, the report displays aspects connected to the quality of the internship experience, the field experience and personal development.

\pagebreak

#Supporting services
We will have some text here.

##Support received before the start of the Erasmus Mundus course

```{r, fig.height = figure_height("B.1.1", course_dataset)}
report_question("B.1.1", course_dataset, text_dataset[,5])
```
```{r, fig.height = figure_height("N.1.1", course_dataset)}
universityprint("N.1.1", course_dataset)
```

##Support received during the orientation program

```{r, fig.height = figure_height("B.1.3", course_dataset)}
report_question("B.1.3", course_dataset, text_dataset[,6])
```
```{r, fig.height = figure_height("N.1.3", course_dataset)}
universityprint("N.1.3", course_dataset)
```

##Helpfulness of units and people

```{r, fig.height = figure_height("B.2.1", course_dataset)}
report_question("B.2.1", course_dataset, text_dataset[,7])
```
```{r, fig.height = figure_height("N.2.1", course_dataset)}
universityprint("N.2.1", course_dataset)
```

##Support received on various issues

```{r, fig.height = figure_height("B.2.2", course_dataset)}
report_question("B.2.2", course_dataset, text_dataset[,8])
```
```{r, fig.height = figure_height("N.2.2", course_dataset)}
universityprint("N.2.2", course_dataset)
```

\pagebreak

#Assessment and feedback
We will have some text here.

##Module assessment

```{r, fig.height = figure_height("C.1", course_dataset)}
report_question("C.1", course_dataset, text_dataset[,9])
```

```{r, fig.height = figure_height("N.3.1", course_dataset)}
universityprint("N.3.1", course_dataset)
```

\pagebreak

#Teaching/learning and supervision
We will have some text here.


##Teaching/learning

```{r, fig.height = figure_height("N.4.1", course_dataset)}
cat(sprintf("\n%s\n", text_dataset[,10]))
universityprint("N.4.1", course_dataset)
```
```{r, fig.height = figure_height("L.4", course_dataset)}
report_question("L.4", course_dataset, text_dataset[,11])
```
```{r, fig.height = figure_height("L.5", course_dataset)}
report_question("L.5", course_datasettext_dataset[,12])
```

\pagebreak

#Internship/field experience and personal development
We will have some text here.

```{r, fig.height = figure_height("L.6", course_dataset)}
report_question("L.6", course_dataset, text_dataset[,13])
```
```{r, fig.height = figure_height("L.3.a", course_dataset)}
report_question("L.3.a", course_dataset, text_dataset[,14])
```
```{r, fig.height = figure_height("L.2.a", course_dataset)}
report_question("L.2.a", course_dataset, text_dataset[,15])
```

\pagebreak

#Acknowledgments

The work of CQAB would not exist and could not continue without the **support of numerous committed volunteers spread all across the world**, driven by a strong motivation to help improve the quality of EMJMD courses. During the last 18 months, over 40 volunteers were involved with different stages of the CQSS project, from analyzing feedback received following the 2013 edition of the CQSS survey, to coding qualitative data and interpreting descriptive graphical information. **CQAB is grateful, humbled and proud to have supported the CQSS project fully through volunteer work**, and thus without external interference.

**Georgiana Mihut** was responsible for the challenging task of coordinating the 40 CQAB volunteers, including chairing most online meetings and manage all the needs, problems and troubles that arise from such a diverse and international group working on a very demanding task. She lead and organized all major steps and tasks during the re-design, implementation and analysis of the survey.

**Mikhail Balyasin** is responsible for the substantial improvements to the design and content of course reports, has skilfully generated the graphical information made available in this report and all others, and created the CQSS interactive online platform. **Luis Carvalho** coordinated the process of analyzing the vast qualitative data that emerged from the CQSS survey, rethought the architecture of the CQSS survey and helped streamline the survey experience for respondents. **Waqas Ahmed** kindly provided ongoing support with tasks that needed a last minute volunteer. **Patrik Punco** and **Haneen Deeb** worked tirelessly to create the online version of the CQSS survey, and became SurveyMonkey experts in the process. Additionally, **Hannen** was involved in the process of restructuring the survey together with Luis. The new version of the CQSS survey benefited from the proofreading skills of **Tugce Schmitt** and **Chiara Dalla Libera**. **Chiara** has graciously facilitated our internal communication before the creation of a communication team. **Kristina Jaksa, Zhanna Saidenova, Sayeeda Amber Sayed, Rediet Tesfaye** and **Hacer Tarcanli** brought an invaluable contribution to the analysis of the qualitative data emerging from the 2015 CQSS survey. Completing the qualitative analysis was far from being a simple task, and their attention to detail, team effort and systematic approach under the coordination of **Luis** serve as an example of good practice in analyzing large sets of qualitative data. 

In the fall of 2015, CQAB conducted a new recruitment process to consolidate its volunteer basis. The new CQAB members provided invaluable contributions towards finalizing the products emerging from the CQSS survey, including the 78 course reports CQAB generated this year. **Aferdita Pustina, Eias Hausen, Felix Donkor, Jacob Sydenham, Joanna Dziadkowiec, Marsela Giovani Husen, Mattia Gusella, Pouneh Eftekhari, Rishikesh Ganjwe, Thuy Van Truong, Tiana Vekic, Tijana Maksimovic, Ana Godonoga, Bishnu Sarker, Chengjia Wang, Daniel Prasetyo, Elizabeth Humberstone, Habtamu Diriba Garomssa, Kseniia Goroshko, Nuoya Chen, Xinyu Wang,** and **Sonja Song** offered meaning and provided text to the numerous graphs that emerged for each course from the quantitative analysis of the CQSS survey. Combined, these volunteers wrote 91,163 words, on average 1169 customized words for each report. Each of them wrote an average of 4144 words. *Primary analyst* for that report is **`r as.character(text_dataset[,2])`** and *secondary analyst* is **`r as.character(text_dataset[,3])`**.


**Muhammad Sohaib Aslam, Wei Wang, Wenjie Shi,** and **Yemi Adeyeye**, members of the newly formed CQAB Communication Team provided support on communication tasks, proofreading and more. **Grischa Fraumann** and **Catherine Lourdes Dy** joined the CQSS task force by provided last minute proofreading help.